A Graph-based Framework for Coverage Analysis in Autonomous Driving \newline \newline Preprint

### 2025-11-18 article/article.tex
some small changes to get it all clean.
subgraph iso app part writing start

\documentclass{article}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{svg}

\title{A Graph-based Framework for Coverage Analysis in Autonomous Driving}
\author{Thomas Mühlenstädt and Marius Bause}
\date{\today}

@@

test4

@@

% The core component is the \texttt{TrainableGraphGINE} class, which implements a Graph Isomorphism Network with Edge features (GINE) architecture for generating graph-level embeddings. The model consists of multiple GINE convolutional layers, each containing:
% \begin{itemize}
%     \item Sequential multi-layer perceptrons (MLPs) with batch normalization and ReLU activations
%     \item Edge-aware message passing incorporating both node and edge features
%     \item Dropout regularization to prevent overfitting
% \end{itemize}

% The model employs a combination of three graph pooling strategies - mean, max, and sum pooling - to create a comprehensive graph-level representation. A projection head enables contrastive learning through InfoNCE loss, while an optional classification head supports supervised learning tasks.

% \subsection{Data Processing and Augmentation}

% The \texttt{GraphDataset} class handles the conversion from NetworkX graphs to PyTorch Geometric format through the \texttt{networkx\_to\_pyg} function. This conversion includes:
% \begin{itemize}
%     \item One-hot encoding of categorical node features (actor types: VEHICLE, PEDESTRIAN, CYCLIST, MOTORCYCLE)
%     \item One-hot encoding of edge types (neighbor\_vehicle, opposite\_vehicle, same\_lane, adjacent\_lane, following, intersection)
%     \item Preservation of continuous features such as longitudinal speed and path length
% \end{itemize}

% Data augmentation is implemented through the \texttt{augment\_graph} function, which adds Gaussian noise to continuous features to create augmented versions for contrastive learning.

% \subsection{Training Methodology}

% The training process utilizes self-supervised contrastive learning with the following characteristics:
% \begin{itemize}
%     \item InfoNCE contrastive loss implemented in the \texttt{contrastive\_loss} function
%     \item Adaptive learning rate schedule with exponential decay (starting at 0.02, decaying by factor 0.75)
%     \item Multi-epoch training with 15 epochs per learning rate stage
%     \item Data from both CARLA simulator (4,442 graphs) and Argoverse 2.0 dataset (3,588 graphs)
% \end{itemize}

% \subsection{Embedding Analysis and Visualization}

% The trained model generates 256-dimensional embeddings for each traffic scene graph. Analysis includes:
% \begin{itemize}
%     \item Dimensionality reduction using Principal Component Analysis (PCA) and t-distributed Stochastic Neighbor Embedding (t-SNE)
%     \item Visualization of embedding space distinguishing between CARLA and Argoverse data sources
%     \item Similarity-based scene retrieval using squared Euclidean distance in embedding space
%     \item Integration with visualization functions (\texttt{plot\_lane\_map\_advanced}, \texttt{add\_actors\_to\_map}, \texttt{add\_actor\_edges\_to\_map}) to display similar traffic scenes
% \end{itemize}

% The implementation demonstrates successful learning of traffic scene representations, with the embedding space capturing meaningful similarities between scenes from different data sources while maintaining distinction between simulation and real-world data.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_carla_coverage_barchart.png}
    \caption{Coverage barchart for the manually defined coverage scenarios for CARLA.}
    \label{fig:subgraph_isomorphism_carla_coverage_barchart}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_agreement_matrix_manual_scenarios_carla.png}
    \caption{Agreement matrix for manually defined coverage scenarios for CARLA.}
    \label{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios_carla}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{plots/combined_distributions_plots_speed_distance_carla.png}
    \caption{Agreement matrix for manually defined coverage scenarios for CARLA.}
    \label{fig:combined_distributions_plots_speed_distance_carla}
\end{figure}

>>>>

\documentclass{article}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{svg}
\usepackage{subcaption}

\title{A Graph-based Framework for Coverage Analysis in Autonomous Driving \newline \newline Preprint}

\author{Thomas Mühlenstädt and Marius Bause}
\date{\today}

@@

tbd

% $$\hat{r} = \frac{N}{E}$$

% $$LL_{\lambda} = \frac{1}{2}\chi^2_{0.025, 2N}$$
% $$UL_{\lambda} = \frac{1}{2}\chi^2_{0.975, 2N + 2}$$

% $$LL_{r} = LL_{\lambda} / E$$
% $$UL_{r} = UL_{\lambda} / E$$

@@

@@

\begin{itemize}
    \item We apply the subgraph isomorphism approach to both the  CARLA and the Argoverse data to identify coverage scenarios.
    \item The archetypes used here are defined manually and described in table xxx. The chosen archetypes are typical traffic situations like e.g. lead vehicle situations, lane change situations or different combinations of opposite direction vehicles.
    \item Also, information like which traffic actors are on an intersection are incorporated into the archetypes.
    \item The results are shown in Figure \ref{fig:subgraph_isomorphism_coverage_barcharts} to Figure \ref{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios_carla}.
    \item In Figure \ref{fig:subgraph_isomorphism_coverage_barcharts} there is a clear signal that for both datasets the coverage is not uniform.
    \item Also, the distribution for the Carla dataset is not close to the Argoverse distribution, indicating that the CARLA data is not representative for the Argoverse data.
    \item Even worse, the Carla dataset is nearly completely missing out e.g. on the cut\_out\_intersection archetype, clearly indicating a coverage gap in the Carla dataset.
\end{itemize}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/subgraph_isomorphism_carla_coverage_barchart.png}
        \caption{CARLA coverage scenarios}
        \label{fig:subgraph_isomorphism_carla_coverage_barchart}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/subgraph_isomorphism_argo_coverage_barchart.png}
        \caption{Argoverse coverage scenarios}
        \label{fig:subgraph_isomorphism_argo_coverage_barchart}
    \end{subfigure}
    \caption{Coverage barcharts for the manually defined coverage scenarios for CARLA and Argoverse.}
    \label{fig:subgraph_isomorphism_coverage_barcharts}
\end{figure}

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.8\textwidth]{plots/subgraph_isomorphism_agreement_matrix_manual_scenarios_carla.png}
%     \caption{Agreement matrix for manually defined coverage scenarios for CARLA.}
%     \label{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios_carla}
% \end{figure}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/subgraph_isomorphism_agreement_matrix_manual_scenarios_carla.png}
        \caption{Agreement matrix for CARLA.}  
        \label{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios_carla}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/subgraph_isomorphism_agreement_matrix_manual_scenarios_argo.png}
        \caption{Agreement matrix for Argoverse.}  
        \label{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios_argo}
    \end{subfigure}
    \caption{Agreement matrix for manually defined coverage scenarios for CARLA and Argoverse.}
    \label{fig:subgraph_isomorphism_agreement_matrix_manual_scenarios}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\textwidth]{plots/combined_distributions_plots_speed_distance_carla.png}
    \caption{Parameter distribution for speed and path length for CARLA.}
    \label{fig:combined_distributions_plots_speed_distance_carla}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\textwidth]{plots/combined_distributions_plots_speed_distance_argo.png}
    \caption{Parameter distribution for speed and path length for Argoverse.}
    \label{fig:combined_distributions_plots_speed_distance_argo}
\end{figure}
